\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
pycgal and pycsg are in C++ not C/C++ (i.e. not C)
del comma

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a 
Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
and \pyinline{pyg4ometry.pycgal} in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using 
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.

>>>>

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a 
Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.
and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using
